---
title: "TreeSpeciesRanking"
author: "William H MacKenzie"
date: "02/10/2019"
output: html_document
---

# Tree Species Environmental Suitability  - March 16, 2019

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require (RGtk2)
require(plyr)
require (rChoiceDialogs)
require (data.table)
require(doBy)
require (utils)
require(labdsv)
require(tools )
require(svDialogs)
require(tcltk)
require(randomForest)
require(foreach)
require(dplyr)
require(reshape2)
require(reshape)
require(doParallel)
require(caret)
require(C50)
require (stringr)
require(UBL)
require(dostats)
require(ordinalForest)
require(tidyverse)
require(ggplot2)
require (RGtk2)

require (rgdal)
require(mapview)
require(sf)
require(tmap)
require(tidyverse)
require(rmapshaper)
require(rgeos)
require(raster)
require(devtools)
#require(cleangeo)

options(stringsAsFactors = FALSE)
## set up some folder location variables
outputs <- ("./outputs/") # location of model outputs 
inputs <- ("./inputs/") 
DB_share <- ("C:/Users/whmacken/Dropbox (WorkingFiles_Telus)/Suitability Review/")
```

## Import All BGC table, Edatopic table extract to create SS to Use table

Table contains all site units for western north america.
```{r import relevant tables, include=FALSE}

ESuit <- fread("./outputs/TreeSpp_ESuit_v11_20_working_AddedCoast_AB.csv")
#ESuit$ESuit <- paste ("E", ESuit$ESuit, sep = "")
#ESuit <- ESuit[!(ESuit$ESuit == "E5"),]
BGCs <- unique(ESuit$BGC)
SS_Use <- fread("D:/CommonTables/BECdb/SiteSeries_Use_CCISSpaper.csv")
SS_Use  <- SS_Use %>% dplyr::select(SS_NoSpace, Use)

Eda <- fread("D:/CommonTables/BECdb/Edatopic_v11_19.csv")

Eda2 <- Eda %>% filter(Edatopic %in% c("B2", "C4", "D6"), is.na(Special)) %>% dplyr::select(Source, BGC, SS_NoSpace, Edatopic) %>% distinct() %>% left_join(.,SS_Use)

fwrite(Eda2, "D:/CommonTables/Becdb/SiteSeries_Use_CCISSpaper2.csv")
## read in previous list


```


## export spatial file suitability rating for review of CCISS paper 
```{r review maps}
SS_Use <- fread("D:/CommonTables/BECdb/SiteSeries_Use_CCISSpaper.csv")
SS.list <- as.list(SS_Use$SS_NoSpace)
#SS_C4 <- SS_Use[SS_Use$Use == "C4",]
#SS_Use$SS_NoSpace <-  as.character(SS_Use$SS_NoSpace)
CCISS_ESuit <- ESuit [SS_NoSpace %in% SS.list,]
CCISS_ESuit <- CCISS_ESuit %>% dplyr::select(SS_NoSpace, Spp, ESuit) %>%
    left_join(.,SS_Use)%>%
    dplyr::select(-Source, -Edatopic, -Special, -Codes) %>%
    dplyr::rename(BGC = MergedBGC)


```
#BGC map themed to species suitability

```{r plot suitability}
WNA_BGC <- readOGR("D:/CommonTables/BGC_Maps/BGCv11_AB_BGCs.shp")
BGC_simple <- rmapshaper::ms_simplify(WNA_BGC, keep = 0.01) 

#Create a dataframe with all a column containing country ID and another with an assigned color:
BGC_col <- data.frame(
  BGC = WNA_BGC$BGC,
  mycolors = c(rep("#e5e5e5",362)), #Assign the same color to all regions initilally
  stringsAsFactors = FALSE
)

#Highlight some selected regions by looking up the 3 letter iso_a3 code and changing the 
#associated hexidecimal color reference:
##For each species
## For each edatope
##Produce output as three panel graphc B2-C4-D6
Spp.list <- c("Hw","Sx")
Spp = "Cw"
SuitCompare <- foreach(Spp = Spp.list, .combine = rbind)  %do% {
  options(stringsAsFactors = FALSE)
Spp_ESuit <- CCISS_ESuit [(CCISS_ESuit$Spp %in% Spp), ]
EdaUse <- unique(Spp_ESuit$Use)
eda = "C4"
  foreach(eda = EdaUse, .combine = rbind) %do%{
    Spp_ESuitEda <- Spp_ESuit [(Spp_ESuit$Use %in% eda), ]
    BGC_col2 <- BGC_col %>% left_join(., Spp_ESuitEda, by = "BGC") %>% distinct()
BGC_col2$mycolors[BGC_col2$ESuit == "1"] <- "#33a02c"
BGC_col2$mycolors[BGC_col2$ESuit == "2"] <- "#faea05"
BGC_col2$mycolors[BGC_col2$ESuit == "3"] <- "#ff7f00"
  WNA_BGC$color <- BGC_col2$mycolors  
  outfile <- paste0 ("./", Spp, "_", eda, ".shp")
shapefile(WNA_BGC,  outfile, overwrite = TRUE)
    
  }
}


WNA_BGC <- readOGR("D:/CommonTables/BGC_Maps/WNA_BGC_v11_31Dec2019.shp")


#Import color selection from region_col dataframe into Europe SpatialPolygonDataFrame
WNA_BGC$color <- BGC_col$mycolors

#Plot resultant map:
qtm(WNA_BGC, fill = "color")

````





## Merge in Reference Guide ratings and footnootes for comparison

```{r import reference guide}
RefGuide <- fread ("D:/CommonTables/ReferenceGuide/ReferenceGuide2019Complete.csv",stringsAsFactors=FALSE)
RefGuide <- RefGuide %>% dplyr::rename(BGC = ZoneSubzone, Spp = Species)
   RefGuide <- drop_na(RefGuide)
### limit refguide to only those units listed in the BECdb
    BECdb <- fread ("D:/CommonTables/BECdb/BEC_SS_v11.csv", stringsAsFactors=FALSE)
    BECdb <- drop_na(BECdb)
###read in accepted units BECv11
RefGuide <- RefGuide[RefGuide$SS_NoSpace %in% BECdb$SS_NoSpace,]
### remove the climate change Standards entries
RefGuide <- RefGuide %>% dplyr::filter(!grepl('CC', Standard))
##update species codes in Ref guide
RefGuide$Spp <- RefGuide$Spp %>% dplyr::recode("Se" = "Sx", "Sw" = "Sx", "Sxw" = "Sx")
#RefGuide <- RefGuide[,c(2:4,9:15)]
#RefCombine <- RefGuide[,c(1:3)]
FullSuitCompare <- merge(ESuit, RefGuide, by.x= c("BGC","SS_NoSpace", "Spp"), by.y = c("BGC","SS_NoSpace", "Spp"), all = TRUE) ##usually set to TRUE
#FullSuitCompare <- FullSuitCompare[(FullSuitCompare$Region == "Nelson") | (FullSuitCompare$Region == "LMH71") | (FullSuitCompare$Region == "LMH702016"), ]
FullSuitCompare <-  FullSuitCompare  %>% distinct() 

###This section simply write a comparison between the reference guide and a table of new ESUITs for review
FullSuitCompare2 <- FullSuitCompare
FullSuitCompare2$ESuit_Ref_same <- FullSuitCompare2$ESuit == FullSuitCompare2$Suitability

colnames(FullSuitCompare2)
data = FullSuitCompare2 %>% dplyr::select(Region,BGC, SS_NoSpace, Standard, Spp, Suitability, ESuit, ESuit_Ref_same, FN1, FN2, FN3, FN4, FN5, FN6,
                         everything())
data <- data[!(data$Region == "NA"),]
write.csv (data, paste0 (DB_share,"ReferenceGuide&ESuit2.csv"), row.names = FALSE )
```
########Bring in Footnote Lookup table
add restriction type variables
```{r footnote type}
footnotes <- fread ("./inputs/FootnoteType.csv")
refguide_footnotes <- as.data.frame (FullSuitCompare[, 19:23])
### converts footnote numbers into a series of footnote types
for ( j in colnames( FullSuitCompare[, 19:23])) { # need to check if these columns align to Footnote columns
for(i in 1: nrow(footnotes)){
  c <- as.integer(footnotes[i,1])
  d <- as.character (footnotes[i,2])
  FullSuitCompare [[j]] [FullSuitCompare [[j]] == c] <- d
  }
}
FullSuitCompare$cold_limit <- apply(FullSuitCompare == "cold", 1, any)
FullSuitCompare$heat_limit <- apply(FullSuitCompare == "heat", 1, any)
FullSuitCompare$drought_limit <- apply(FullSuitCompare == "drought", 1, any)
FullSuitCompare$wet_limit <- apply(FullSuitCompare == "wet", 1, any)
FullSuitCompare$geographic_limit <- apply(FullSuitCompare == "geographic", 1, any)
FullSuitCompare$trial_spp <- apply(FullSuitCompare == "trial", 1, any)
FullSuitCompare <- as.data.frame (FullSuitCompare[,-c(19:23)])

FullSuitCompare <- merge (FullSuitCompare, refguide_footnotes, by = 0) # add back in the original FN numbers
#ESuit <- rbind (ESuit, ESuit4) ### use where combining multiple suitability sheets
FullSuit.list <- unique(FullSuitCompare$Unit)
```


## Generate site level CMD from climate surface derived data
LHC_training set is generated from ##### script
```{r import climate}
temp2 <- fread("./inputs/ALLBGC_cLHS_12vars_Esuit.csv", data.table = FALSE,stringsAsFactors=FALSE)
colnames (temp2)[2] <- "BGC"
temp2 <- temp2[-1]

CMD <- aggregate( CMD.total ~ BGC, temp2, mean) ##
meanVar <-aggregate( . ~ BGC, temp2, mean)
SS_Var <- merge(FullSuitCompare, meanVar, by = "BGC")
SS_Var$Spp [is.na(SS_Var$Spp)] <- "X" ### where no treespecies suitable create a no-species code 'X'

###_____________________________________________####

###for each wetter rSMR, previous CMD is divided by 2
for (i in 1:3){
  CMD[,2+i] <- CMD[,1+i]/2
}
colnames(CMD) <- c("BGC","4","5","6","7")
CMD <- CMD[,c(1,3:5,2)]

###for each drier rSMR, previous CMD + 100
for (i in 1:4){
  CMD[,length(CMD)+1] <- CMD[,length(CMD)] + 100
}
colnames(CMD)[6:9] <- c("3","2","1","0")

CMD <- CMD[,order(colnames(CMD))]## creates full grid of CMD values by BGC by rSMR class

CMD.list <- melt(CMD)
 #######needs to get rid of blank BGC
CMD.list$EDA <- paste (CMD.list$BGC, "_", CMD.list$variable)
CMD.list <- CMD.list[,-c(1:2)] 
```


## Import edatopic and aSMR tables

Merge all climate and edatopic variables with suitability ratings

```{r import edaphic}

E1 <- fread (paste0(DB_share,"Edatopic_v11_9.csv"),stringsAsFactors=FALSE , na.strings= c("", "NA"))

#E2 <- E1 %>% distinct()
#write.csv (E2, "Edatopic_v11.2.csv")
#E1 <- E1[,-c(5)]
#E1 <- E1 [is.na (E1$Codes),]### removes site series flagged with special condition
E1 <- unique(E1)
Codes <- unique (E1[,c(3,6)]) ## identify special ecosystems
colnames (Codes) [1] <- "Unit"

E1$SNR <-str_sub(E1$Edatopic, 1,1)
E1$rSMR <-str_sub(E1$Edatopic, -1,-1)
E1$EDA <- paste (E1$MergedBGC, "_", E1$rSMR)
E1_sub <- E1 [E1$EDA %in% CMD.list$EDA,]
E1_sub <- merge (E1_sub, CMD.list, by = "EDA")
names(E1_sub) [10] <- "EdaCMD"
E1_sub$EdaCMD <- as.numeric(E1_sub$EdaCMD)
E2 <- E1_sub
#E1_sub$SNR <- as.factor(E1_sub$SNR)
E1_sub$SNR_num <- E1_sub$SNR%>% str_replace_all(c("A" = "1", "B" = "2", "C" = "3", "D" = "4" ,"E" = "5" ))
E1_sub$SNR_num <- as.numeric(E1_sub$SNR_num)

 
aSMRrSMR = "./inputs/modelled_ALLv11_rSMR_aSMR_grid_HalfStep.csv"
aSMR <- fread(aSMRrSMR,stringsAsFactors=FALSE,na.strings=".")
aSMR <- aSMR[,-1]
colnames(aSMR) <- c("BGC","0","1","2","3","4","5","6","7")
aSMR.list <- melt(aSMR)
aSMR.list$EDA <- paste (aSMR.list$BGC, "_", aSMR.list$variable)
aSMR.list <- aSMR.list [,-c(1:2)]
E1_sub <- merge (E1_sub, aSMR.list, by = "EDA")
colnames (E1_sub)[12] <- "aSMR"
E1_sub <- E1_sub [, c("SS_NoSpace", "EdaCMD", "SNR_num", "aSMR")]#
E1_sub <- E1_sub %>% distinct()
E1_sub$SS_NoSpace <- as.character(E1_sub$SS_NoSpace)
SS_data <- E1_sub[,-1] %>% group_by(E1_sub$SS_NoSpace) %>% summarise_all(list(~min(.),~mean(.),~max(.), ~sd(.)))###ignore warning
#SS_data <- SS_data [-2]
colnames(SS_data)[1] <- "SS_NoSpace"
SS_test <- merge (SS_Var, SS_data, by = "SS_NoSpace")
difs <- setdiff(SS_Var$SS_NoSpace,SS_data$SS_NoSpace) ### look for units no matching between 2 tables
difs
#difs2 <- setdiff(SS_data$Unit,SS_Var$Unit)
#difs2
SS_test <- SS_test[!is.na(SS_test$Spp),]
SS_test$ES_RG_same <- SS_test$ESuit == SS_test$RefSuit
data = SS_test %>% select(Region, BGC, Unit, Spp, ESuit, RefSuit, ES_RG_same,
                          cold_limit, heat_limit,drought_limit,wet_limit, geographic_limit, 
                          FN1, FN2, FN3, FN4, FN5,
                         EdaCMD_max, aSMR_min, aSMR_max, Tmin_sp,  bFFP, PAS)
data <- data %>% distinct()
write.csv (data, "./outputs/SS_Suit_for_Review.csv")
```

### Compare to  A Banners original ratings
Limit to Esuit rating he provided.
Add in flag variable to show where differs from current ratings

``` {r merge with draft suitability ratings - ABanner}

AB_Suit <- fread("./inputs/TreeSppSuit_v10.10_AB.csv")
AB_Suit.list <- melt(AB_Suit)
colnames (AB_Suit.list) [2:3] <- c("Spp", "AB_suit")
AB_Suit.list <- AB_Suit.list %>% drop_na()
SS_test2 <- merge (SS_test, AB_Suit.list, by = c("Unit", "Spp"))
SS_test2$ES_AB_same <- SS_test2$ESuit == SS_test2$AB_suit
SS_test2$ES_RG_same <- SS_test2$ESuit == SS_test2$RefSuit
colnames(SS_test2)
data = SS_test2 %>% select(BGC, Unit, Spp, ESuit, AB_suit, ES_AB_same, RefSuit, ES_RG_same, 
                          cold_limit, heat_limit,drought_limit,wet_limit, geographic_limit,
                          FN1, FN2, FN3, FN4, FN5,
                         EdaCMD_max, aSMR_min, aSMR_max, Tmin_sp,  bFFP, PAS)
data <- data %>% distinct()

write.csv (data, "./outputs/ESuit_review_AB.csv")
```




## Estimated relative site index (by site condition)

Need input table of relative site index by aSMR x SNR
Add the SI % value to each edatopic position in E1 for each species
Turn into actual Site Index Values by multiplying by GDD based factor
Summarize by site series (mean plus SD)


``` {r estimated site index}
rSI <- fread ("./inputs/rSI_by_Edatope.csv") # this is a heuristic approximation of relative site index on a absolute grid
<<<<<<< HEAD
rSI$aEdatopic <- paste0(rSI$SNR, rSI$aSMR)
rSI <- as.data.frame (rSI)
DD5 <- fread ("./inputs/DD5_BGC.csv") # growing degree days by BGC
E2_sub <- merge (E2, aSMR.list, by = "EDA")
colnames (E2_sub)[11] <- "aSMR"
E2_sub$aEdatopic  <- paste0(E2_sub$SNR, E2_sub$aSMR)
setnames(E2_sub, "MergedBGC", "BGC")
# add in DD5 values by BGC
E2_sub <- left_join(E2_sub, DD5, by = "BGC")

spps <- unique(rSI$Spp)
BGCs <- unique (E2_sub$MergedBGC)
#spp = "Fd"
####need to change into a foreach and the rbind to get final table
for (spp in spps){
  SS.temp <- ESuit$Unit[ESuit$Spp == spp]
  Suit.temp <- E2_sub [E2_sub$SS_NoSpace %in% SS.temp,]
  rSI.temp <- rSI [,c(4:5)] [rSI$Spp %in% spp,]
  Suit.temp <- left_join(Suit.temp, rSI.temp, by = "aEdatopic")#  ### add in rSI values to each line
  Suit.temp$SI <- Suit.temp$rSI *(Suit.temp$DD5 * 0.022)  ### multiply rSI * formula to new variable to get SI
  ### Need to adjust for excessive heat limitations to growth
  Suit.temp <- Suit.temp %>% 
  select(BGC, SS_NoSpace, SI)
  SI.temp <- Suit.temp [-2] %>% group_by(Suit.temp$SS_NoSpace) %>% summarise ( SI_mean = mean(SI), SI_sd = sd(SI)) 
  SI.temp$Spp <- spp

}


# formula for SI = rSI * (DD5 *.022)relative SI into a SI50 value for Fd

DD5 <- fread ("./inputs/DD5_BGC.csv") # growing degree days by BGC
E2_sub <- merge (E2, aSMR.list, by = "EDA")
colnames (E2_sub)[11] <- "aSMR"

spps <- unique(rSI$Spp)
BGCs <- unique (E2_sub$MergedBGC)
spp = "Fd"
for (spp in spps){
  SS.temp <- ESuit$Unit[ESuit$Spp == spp]
  Suit.temp <- E2_sub [E2_sub$SS_NoSpace %in% SS.temp,]
  ### add in RSI values to each line
  ### multiply RSI * formula to new variable to get SI
  ###summarize SI by site series mean and sd
  
  
  
  for(edatope in edatopes){
    comm.ref <- get(paste("comm.ref", edatope, sep=""))
    comm.ref.spp <- comm.ref>0
    
    for(rcp in rcps){
      for(proj.year in proj.years){

        comm.proj <- as.data.frame(matrix(rep(NA, dim(points)[1]*length(spps)), dim(points)[1], length(spps)))
        for(spp in spps){
          Suit <- read.csv(paste("outputs/Suit", grid, GCM, rcp, proj.year, spp, edatope, "csv", sep="."))[,1]
          Suit[Suit==4] <- 5
          Suit <- 1-(Suit-1)/4
          comm.proj[,which(spps==spp)] <- Suit
        }    
    
    


E2_sub2 <- E2_sub2[E2_sub$MergedBGC %in% ESuit$Unit[ESuit$Spp == "Fd"]] <- rSI$rSI
E1_sub <- E1_sub [, c("SS_NoSpace", "EdaCMD", "SNR_num", "aSMR")]#
E1_sub <- E1_sub %>% distinct()
E1_sub$SS_NoSpace <- as.character(E1_sub$SS_NoSpace)
E2 <- merge(E1, )
SS_edatope <- 
#Add the equivalent aSMR to rSI
# formula for SI = rSI * (DD5 *.022)relative SI into a SI50 value

```

## Create edatopic grid review materials 

On edatopic grid show species suitable by edatopic position
Suitability rating
Site Index
aSMR

```{r Edatopic Review}
SIdat <- fread("./inputs/BartPredSI.csv", data.table = F)
edaDat <- fread("./inputs/Edatopic_v11_7.csv", data.table = F)
edaDat <- edaDat[edaDat$Source %in% c("BECv10","BECv11"),c("MergedBGC", "SS_NoSpace","Edatopic")]
suitDat <- fread("./inputs/TreeSpp_ESuit_v11_18.csv", data.table = F)
suitDat <- suitDat[suitDat$Unit %in% unique(edaDat$SS_NoSpace),c("Unit","Spp","ESuit")]
SIdat <- SIdat[,-4]

dat <- merge(SIdat, suitDat, by = c("Unit","Spp"), all = T)
dat <- dat[!is.na(dat$SIPred),]
dat <- dat[!is.na(dat$ESuit) | dat$SIPred >= 20,]
dat$ESuit[is.na(dat$ESuit)] <- 5
colnames(edaDat) <- c("Subzone","Unit","Edatopic")
edaDat <- unique(edaDat)
dat <- merge(dat, edaDat, by = "Unit", all.x = T)
dat$SIPred <- round(dat$SIPred,1)
dat <- unique(dat)
dat <- dat[!is.na(dat$Edatopic),]


out <- foreach(BGC = unique(dat$Subzone), .combine = rbind) %do% {
  sub <- dat[dat$Subzone == BGC,]
  gridDat <- foreach(eda = unique(sub$Edatopic), .combine = rbind) %do% {
    sub2 <- sub[sub$Edatopic == eda,]
    temp <- aggregate(cbind(SIPred, ESuit) ~ Spp + Edatopic, sub2, FUN = mean) %>%
      mutate(SIPred = round(SIPred,1), ESuit = round(ESuit, 0))
    temp <- temp[order(-temp$SIPred),]
    temp$Spp <- paste(temp$Spp,temp$SIPred, sep = ":")
    if(any(temp$ESuit == 1)){
      dom <- paste(temp$Spp[temp$ESuit == 1], collapse = ",")
      dom <- paste("*",dom,"*\n", sep = "")
    }else{
      dom <- NULL
    }
    if(any(temp$ESuit == 2)){
      sec <- temp$Spp[temp$ESuit == 2]
      sec <- paste(sec, collapse = ",")
      sec <- paste(sec,"\n")
    }else{
      sec <- NULL
    }
    if(any(temp$ESuit == 3)){
      un <- temp$Spp[temp$ESuit == 3]
      un <- paste(un, collapse = ",")
      un <- paste("(",un,")\n", sep = "")
    }else{
      un <- NULL
    }
    if(any(temp$ESuit %in% c(4,5))){
      x <- temp$Spp[temp$ESuit %in% c(4,5)]
      x <- paste(x,",",sep = "")
      if(length(x) >= 2){
        j <- 0
        for(i in seq(2,length(x), by = 2)){x <- append(x,"\n", after = i+j);j <- j+1}
      }
      if(x[length(x)] == "\n"){x <- x[-length(x)]}
      x <- paste(x, collapse = "")
      x <- paste("[",x,"]", sep = "")
    }else{
      x <- NULL
    }
    lab <- paste(dom, sec,  un,x, sep = "")
    
    data.frame(Edatopic = eda, Label = lab)
  }
  gridDat$Alpha <- gsub("[[:digit:]]","",gridDat$Edatopic)
  gridDat$Numeric <- gsub("[[:upper:]]","",gridDat$Edatopic) %>% as.numeric()
  ##plot
  pdf(file = paste("./outputs/SIGrid_",BGC,".pdf",sep = ""), height = 10.5, paper = "letter")
  print(ggplot(data = gridDat)+
          geom_tile(aes(x= Alpha, y = Numeric), color = "black", fill = "white")+
          geom_text(aes(x = Alpha, y = Numeric, label = Label), size = 2.4)+
          scale_y_discrete(limits = c("8","7","6","5","4","3","2","1","0"))+
          scale_x_discrete(limits = c("A","B","C","D","E"))+
          labs(x = "Relative Soil Nutrient Regime", y = "Relative Soil Moisture Regime", cex = 1.5, title = BGC)+
          theme_bw(base_size = 10)+
          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
          coord_fixed())
  dev.off()
  gridDat
}
