---
title: "Species_Environment_Curves"
author: "Kiri Daust/Will MacKenzie"
date: "15/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#### Fit distribution curves of tree species to climate variable based on BEC plot data
#### Kiri Daust May 2020

library(data.table)
library(tidyverse)
#library(sf)
library(raster)
library(ggstance) ##need this for boxplot
library(foreach)
library(weights)
library(minpack.lm) ##this nls algorithm is better
library(sn)
library(ggthemes)
library(gridExtra)
library(Rcpp)
require(stats)

#setwd("D:/GitHub/TreeSuitabilityPrediction/")


aspectCalc1 <- function(lat, slope, aspect){##eqn 1 from McCune 2007
  lat <- lat*pi/180
  slope <- slope*pi/180
  aspect <- aspect*pi/180
  HL <- abs(pi - abs(aspect - (5*pi)/4))
  res <- -1.467+1.582*cos(lat)*cos(slope)-1.5*cos(HL)*sin(slope)*sin(lat)-0.262*sin(lat)*sin(slope)+0.607*sin(HL)*sin(slope)
  return(exp(res))
}

aspectCalc2 <- function(lat, slope, aspect){##eqn 2 from McCune 2007
  lat <- lat*pi/180
  slope <- slope*pi/180
  aspect <- aspect*pi/180
  HL <- abs(pi - abs(aspect - (5*pi)/4))
  res <- -1.236+1.35*cos(lat)*cos(slope)-1.376*cos(HL)*sin(slope)*sin(lat)-0.331*sin(lat)*sin(slope)+0.375*sin(HL)*sin(slope)
  return(exp(res))
}

aspectCalc3 <- function(lat, slope, aspect){##eqn 3 from McCune 2007
  lat <- lat*pi/180
  slope <- slope*pi/180
  aspect <- aspect*pi/180
  HL <- abs(pi - abs(aspect - (5*pi)/4))
  res <- 0.339+0.808*cos(lat)*cos(slope)-0.196*sin(lat)*sin(slope)-0.482*cos(HL)*sin(slope)
  return(res)
}

###change the name of aspectCalc in this function to use a different equation
aspectRatio <- function(lat,slope,aspect,refSlope = 20, refAspect = 45){
  new <- aspectCalc3(lat,slope,aspect)
  standard <- aspectCalc3(lat = lat, slope = refSlope, aspect = refAspect)
  return(new/standard)
}

##modified function from US script
removeOutlier <- function(dat, alpha,numIDvars){
  out <- foreach(curr = unique(as.character(dat$Zone)), .combine = rbind) %do% {
  #out <- foreach(curr = unique(as.character(dat$BGC)), .combine = rbind) %do% {
    temp <- dat[dat$Zone == curr,]
    md <- tryCatch(mahalanobis(temp[,-c(1:numIDvars),with = F],
                               center = colMeans(temp[,-c(1:numIDvars), with = F]), 
                               cov = cov(temp[,-c(1:numIDvars), with = F])), error = function(e) e)
    if(!inherits(md,"error")){
      ctf <- qchisq(1-alpha, df = ncol(temp)-1)
      outl <- which(md > ctf)
      cat("Removing", length(outl), "outliers from",curr, "; ")
      if(length(outl) > 0){
        temp <- temp[-outl,]
      }
    }
    temp
    
  }
  return(out)
}

paste3 <- function(...,sep="") {
     L <- list(...)
     L <- lapply(L,function(x) {x[is.na(x)] <- ""; x})
     ret <-gsub(paste0("(^",sep,"|",sep,"$)"),"",
                 gsub(paste0(sep,sep),sep,
                      do.call(paste,c(L,list(sep=sep)))))
     is.na(ret) <- ret==""
     ret
}

##recursive function to adjust CMD based on rSMR
adjCMD <- function(CMD,rSMR, currLevel){
  if(currLevel == rSMR){
    return(CMD)
  }else if(currLevel < rSMR){
    adjCMD(CMD/2,rSMR,currLevel + 1)
  }else{
    adjCMD(CMD+100,rSMR,currLevel-1)
  }
}

##C++ function to lookup aSMR rules
cppFunction('NumericVector calcASMR(NumericVector rSMR,NumericVector CMD, DataFrame Rules) {
  NumericVector rSMRLev = Rules["SMRLevel"];
  NumericVector CMDctf = Rules["CMD"];
  NumericVector aSMR = Rules["aSMR"];
  int len = CMD.length();
  IntegerVector v;
  NumericVector out(len);
  for(int i = 0; i < len; i++){
    v = Rcpp::seq(0, aSMR.length()-1);
    if(rSMR[i] < 5){
      v = v[rSMRLev == 0];
    }else if(rSMR[i] == 5){
      v = v[rSMRLev == 5];
    }else if(rSMR[i] == 6){
      v = v[rSMRLev == 6];
    }else{
      v = v[rSMRLev == 7];
    }
    int j;
    for(j = v[0]; j < v[v.length()-1]; j++){
      if(CMD[i] <= CMDctf[j]){
        break;
      }
    }
    out[i] = aSMR[j];
  }
  return(out);
}')

```

##load and clean data
```{r load data}
###USA FIA data#####
us_veg <- fread("./InputData/AllUSandFIA16Apr2020_Veg.csv")
cols <- grep("Cover",colnames(us_veg))[1:4] ##only include cover 1,2,3,4
us_veg <- us_veg[,c(1,2,cols), with = F]
us_veg[,Cover := rowSums(.SD, na.rm = T),.SDcols = -c("PlotNumber","Species")]
us_veg <- us_veg[,.(PlotNumber,Species,Cover)]

#bc_veg <- fread("./InputData/BECMaster19_Veg.csv")
load("./InputData/VegDat_Clean.RData")
bc_veg <- vegData
# cols <- grep("Cover",colnames(bc_veg))[1:4] ##only include cover 1,2,3,4
# bc_veg <- bc_veg[,c(1,2,cols), with = F]
# bc_veg <- bc_veg[,Cover := rowSums(.SD, na.rm = T),.SDcols = -c("PlotNumber","Species")]
#bc_veg <- bc_veg[Cover > 0,.(PlotNumber,Species,Cover)]

envAll <- fread("./InputData/BECMaster19_Env.csv")
us_env <- fread("./InputData/AllUSandFIA16Apr2020_Env.csv")
envAll <- rbind(envAll, us_env)
vegData <- rbind(bc_veg, us_veg)
climDat <- fread("./InputData/EcoPlot_Locations_Normal_1961_1990MSY.csv")#, select = c("ID1","ID2","Latitude","Longitude", "Elevation"))
climDat <- climDat[!duplicated(climDat, by = "ID1"),]##remove US plots with same PlotNumber
#fwrite(climDat ,"EcoPlot_Locations.csv")
##BGC climate data
# bgcDat <- fread("BGC_ClimDat_Veg_2000-2018.csv",select = c("Year", "ID1","ID2","Latitude", "DD5","Tmax_sm","FFP","Tave_sm","Tmin_wt","CMD"))
# bgcDat <- bgcDat[Year %in% 2000:2018,]
# bgcDat <- bgcDat[,lapply(.SD,mean),by = .(ID1,ID2,Latitude), .SDcols = -("Year")]
# fwrite(bgcDat,"BGC_ClimDat_Veg_2000-2018.csv")

##Prepare data
envAll <- envAll[Date > as.Date("2001-01-01"),] ##remove old plots
vegData <- vegData[vegData$Cover >= 0.2,] ### remove entries with low cover
envPlt <- unique(envAll$PlotNumber)
vegData <- vegData[vegData$PlotNumber %in% envPlt,]
envAll <- envAll[envAll$PlotNumber %in% vegData$PlotNumber,]

plotBGC <- envAll[Aspect >= 0 & Aspect <= 360,
                  c("PlotNumber","Longitude","Latitude","Zone","SubZone","SiteSeries","MoistureRegime","NutrientRegime","SlopeGradient","Aspect")]
vegSub <- merge(vegData, plotBGC, by = "PlotNumber")
vegSub <- vegSub[!is.na(vegSub$Longitude) & !is.na(vegSub$SlopeGradient),]
#vegSub$Aspect[vegSub$SlopeGradient == 0] <- 180
vegSub <- vegSub[!is.na(vegSub$Aspect) & vegSub$Aspect != 999 & vegSub$SlopeGradient != 999,] ##remove 999
#covert to degrees - part of function?
vegSub$Slope <- atan(vegSub$SlopeGradient/100)
vegSub$Slope <- vegSub$Slope*180/pi ##to radians
vegSub$Slope <- ifelse(vegSub$Slope >45, 45, vegSub$Slope) ##max limit on slope in calculation
##calculate aspect ratio of vegetation datalat = vegSub$Latitude,
vegSub$AspectRatio <- aspectRatio(lat = vegSub$Latitude, slope = vegSub$Slope, aspect = vegSub$Aspect)

###load BEC climate data
bgcDat <- fread("D:/CommonTables/HexGrids/WNAv12_HexGrid_2km_Normal_1961_1990MSY.csv")
suitAll <- fread("./inputs/Feasibility_v11_21.csv")

sppLookup <- fread("./inputs/TreeCrosswalk.csv")
```

##Choose species and variables
```{r select species and variables}
climSub <- climDat %>% dplyr::select(ID1, DD5_sm, Tmax_sm, FFP,Tave_sm,Tmin_wt,CMD,PPT_at,PPT_wt) ##select climate variables
veg_only <- vegSub %>% dplyr::select(-Longitude, -SiteSeries)
vegClim <- left_join(veg_only, climSub, by = c("PlotNumber" = "ID1"))
vegClim2 <- vegClim %>% na_if(-9999.0) %>% drop_na() %>% as.data.table()
##apply aspectratio adjustment to climate variables
vegClim2[,c('DD5_sm','Tmax_sm','CMD', "MCMT") := .(DD5_sm*AspectRatio,Tmax_sm*AspectRatio,Tave_sm*AspectRatio,CMD*AspectRatio)]
vegAll <- vegClim2
```


##Loop though species and variables, output faceted figure and create data table of suitability

```{r loops, fig.width=10, fig.height=11}
species <- c("Pl","Fd","Sx")#, "Pw", "Py", "Bg")
vars <- c("MCMT", "DD5_sm")
minNumPlots <- 10 ##remove bins where there are few plots in total

out <- foreach(sppCode = species, .combine = c) %do% {
  foreach(var = vars, .combine = c) %do% {
    spp <- sppLookup$Code[sppLookup$TreeCode == sppCode]
    
    bgDat <- bgcDat[,c("BGC","Latitude",var), with = F]
    colnames(bgDat)[3] <- "Var"
    ##remove outliers
    bgDat <- bgDat[, 
        .SD[(Var < quantile(Var, probs = 0.90)) & ((Var > quantile(Var, probs = 0.10)))
        ], by = BGC
    ]
    
    t1 <- aspectRatio(lat = bgDat$Latitude, slope = 30, aspect = 135)
    bgDat$Neutral <- bgDat$Var*t1 ###"neutral" aspect
    t1 <- aspectRatio(lat = bgDat$Latitude, slope = 30, aspect = 225)
    bgDat$Warm <- bgDat$Var*t1 ###"warm" aspect
    bgAvg <- bgDat[,.(MeanCld = mean(Var),MeanNt = mean(Neutral),MeanWrm = mean(Warm)), by = "BGC"]
    bgDat <- bgDat[BGC %in% c("BAFAun", "CMAun", "BWBSdk", "ESSFmc", "SBSdk", "SBSmc2", "ICHmc2","IDFdk3", "PPxh1", "CWHdm", "CWHvm1" ,"BGxh_WA")]
    bgDat <- bgDat[order(BGC),]
    
    suit <- suitAll[Spp == sppCode,.(BGC,SS_NoSpace,Spp,Feasible)]
    suit <- suit[grep(".*01|.*101",SS_NoSpace),.(BGC,Feasible)]
    cols <- data.table(Feasible = c(1,2,3,4,5),col = c("green","yellow","red","brown","brown"))
    suit2 <- suit[cols, on = "Feasible", nomatch = 0]
    
    cols <- data.table(BGC = unique(bgDat$BGC))
    cols <- suit2[cols, on = "BGC"]
    cols$col[is.na(cols$col)] <- "brown"
    
    veg <- vegAll %>% filter(Species == spp) %>% droplevels() %>% dplyr::select(-c(Latitude,Zone,SubZone,MoistureRegime,NutrientRegime,PPT_at,PPT_wt))
    
    dat <- veg %>% mutate_if(is.integer, as.numeric)
    dat2 <- dat[,-c(1:7)]
    numIDvars = 7
    alpha = .05
    md <- mahalanobis(dat2,
                           center = colMeans(dat2), 
                           cov = cov(dat2))
    
    ctf <- qchisq(1-alpha, df = ncol(dat)-1)
    outl <- which(md > ctf)
    dat <- dat[-outl,]
    veg <- dat
    
    brk <- seq(min(vegAll[[var]]),max(vegAll[[var]]),length.out = 25)
    matHistAll <- hist(vegAll[[var]], breaks = brk,plot = F) ##create histogram of all plots for specified variable
    histAll <- matHistAll$counts
    
    vegHist <- wtd.hist(veg[[var]], plot = F,weight = veg$Cover, breaks = brk)
    
    brk <- brk[histAll > minNumPlots]
    h <- vegHist$counts[histAll > minNumPlots]/histAll[histAll > minNumPlots] ##ratio of weighted veg hist to total num plots in each bin
    if(length(brk) > length(h)){brk <- brk[-1]} ##depending on the variable sometimes breaks don't line up
    
    dat <- data.frame(x = brk, r = h) ##create data for nls
    muStart <- brk[h == max(h) ] ###starting values for optimisation
    sdStart <- muStart/4
    kStart <- muStart/2
    
    fit <- nlsLM(r ~ k * dsn(x,xi = mu,omega = sigma, alpha = a), start=c(mu=muStart,sigma=sdStart,k=kStart,a = 1) , # a=0
                 data = dat)
    v <- summary(fit)$parameters[,"Estimate"] ###v contains the 4 parameters for the best fit curve
    plotNrm <- function(x) {v[3] * dsn(x, v[1],v[2],v[4])}
    mX <- optimize(plotNrm, interval = c(min(dat$x-10),max(dat$x + 10)), maximum = T) ##find maximum
    probMx <- psn(mX$maximum,xi = v[1],omega = v[2],alpha = v[4]) ##find area below maximum
    ##set up quantiles for colouring
    quants <- qsn(c(probMx/10,probMx/2,probMx+(1-probMx)*0.5,probMx+(1-probMx)*0.9),xi = v[1],omega = v[2],alpha = v[4])
    quants <- c(min(dat$x-10),quants,max(dat$x + 10))
    if(quants[1] > quants[2]){quants[1] <- quants[2]-10}
    if(quants[6] < quants[5]){quants[6] <- quants[5]+10}
    lims <- qsn(c(0.01,0.99),xi = v[1],omega = v[2],alpha = v[4])
    
    bgAvgAll <- bgAvg
    bgAvg <- bgAvg[suit, on = "BGC"]
    bgAvg <- bgAvg[!is.na(MeanCld),]
    ctfLow <- min(bgAvg$MeanCld[bgAvg$Feasible == 1])
    horizLow <- plotNrm(ctfLow)
    ctfHigh <- max(bgAvg$MeanWrm[bgAvg$Feasible == 1])
    
    ##I know this code looks awful, but it's actually computationally efficient (much more than ifelse e.g.)
    bgAvgAll[,c("Cold","Neutral","Warm") := .(NA,NA,NA)]
    bgAvgAll$Neutral[bgAvgAll$MeanNt < ctfLow] <- "-N"
    bgAvgAll$Neutral[bgAvgAll$MeanNt < lims[1]] <- "--N"
    bgAvgAll$Neutral[bgAvgAll$MeanNt > ctfHigh] <- "+N"
    bgAvgAll$Neutral[bgAvgAll$MeanNt > lims[2]] <- "++N"
    bgAvgAll$Cold[bgAvgAll$MeanCld < ctfLow] <- "-C"
    bgAvgAll$Cold[bgAvgAll$MeanCld < lims[1]] <- "--C"
    bgAvgAll$Cold[bgAvgAll$MeanCld > ctfHigh] <- "+C"
    bgAvgAll$Cold[bgAvgAll$MeanCld > lims[2]] <- "++C"
    bgAvgAll$Warm[bgAvgAll$MeanWrm < ctfLow] <- "-W"
    bgAvgAll$Warm[bgAvgAll$MeanWrm < lims[1]] <- "--w"
    bgAvgAll$Warm[bgAvgAll$MeanWrm > ctfHigh] <- "+W"
    bgAvgAll$Warm[bgAvgAll$MeanWrm > lims[2]] <- "++W"
    
    outTable <- bgAvgAll[,.(BGC,Cold,Neutral,Warm)]
    outTable[,c('Spp','Var') := .(sppCode,var)]
    
    colScale <- cols$col
    names(colScale) <- cols$BGC
    
    ##plot response curve
    p1 <- ggplot(dat)+
      geom_point(aes(x = x, y = r),color = "black")+
      stat_function(fun = plotNrm, colour = "black")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[3],quants[4],0.1)),x = seq(quants[3],quants[4],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "green")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[2],quants[3],0.1)),x = seq(quants[2],quants[3],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[4],quants[5],0.1)),x = seq(quants[4],quants[5],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[1],quants[2],0.1)),x = seq(quants[1],quants[2],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[5],quants[6],0.1)),x = seq(quants[5],quants[6],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
      geom_vline(xintercept = ctfLow)+
      geom_vline(xintercept = ctfHigh)+
      geom_hline(yintercept = horizLow)+
      xlim(lims)+
      ylim(c(0,NA))+
      labs(y = "Standardised Frequency", title = paste(spp, var))+
      theme_few()+
      theme(axis.title.x = element_blank(),
            axis.text.x = element_blank())
    
    p2 <- ggplot(bgDat,aes(y = BGC,group = BGC,col = BGC))+
      geom_boxploth(aes(x = Neutral))+
      geom_boxploth(aes(x = Warm))+
      geom_boxploth(aes(x = Var))+
      scale_colour_manual(values = colScale)+
      xlim(lims)+
      geom_vline(xintercept = ctfLow)+
      geom_vline(xintercept = ctfHigh)+
      labs(y = "BGC", x = var)+
      theme_few()+
      theme(legend.position = "none")
    
    outPlt <- cowplot::plot_grid(p1, p2, align = "v", ncol = 1, rel_heights = c(0.66, 0.34))
    list(Graph = outPlt, Data = outTable)
  }
}
grList <- out[seq(1,length(species)*length(vars)*2,by = 2)]
dat <- do.call(rbind, out[seq(2,length(species)*length(vars)*2,by = 2)])
dat[, Suit := paste3(Cold,Neutral,Warm)]
dat$Suit[is.na(dat$Suit)] <- "OK"
dat$Suit[!is.na(dat$Cold)&!is.na(dat$Neutral)&!is.na(dat$Warm)] <- "X" ##suitability codes
grid.arrange(grobs = grList, ncol = 3) ##plot
```

### Calculate aSMR
```{r aSMR}
SMRdat <- vegAll[!is.na(MoistureRegime) & MoistureRegime!= "",-c("Species","Cover","DD5","Tmax_sm","Tave_sm","FFP","Tmin_wt")] %>% unique()
SMRdat$PPT.dorm <- SMRdat$PPT_at + SMRdat$PPT_wt
SMRdat$Def <- 300 - SMRdat$PPT.dorm ###adds deficit from incomplete recharge in dormant season. 
SMRdat$Def[SMRdat$Def < 0] <- 0
SMRdat$CMD <- SMRdat$CMD + SMRdat$Def
SMRdat$MoistureRegime <- gsub("\\D","",SMRdat$MoistureRegime)
SMRdat$MoistureRegime <- gsub("^(.{1}).*","\\1",SMRdat$MoistureRegime) %>% as.numeric()
SMRdat <- SMRdat[complete.cases(SMRdat),]

### adjust CMD based on rSMR
SMRdat$CMD2 <- apply(SMRdat[,.(CMD,MoistureRegime)],MARGIN = 1,FUN = function(x){adjCMD(x[1],x[2],4)})
rules <- fread("./inputs/aSMR_Rules_HalfStep.csv")

### Calculate aSMR from ruleset
SMRdat$aSMR <- calcASMR(SMRdat$MoistureRegime,SMRdat$CMD2,rules)
SMRdat <- SMRdat[,.(PlotNumber,NutrientRegime,aSMR)]

SMRdat$NutrientRegime <- gsub("^(.{1}).*","\\1",SMRdat$NutrientRegime) %>% toupper()
SMRdat <- SMRdat[NutrientRegime %in% c("A","B","C","D","E","F"),]
```

### Generate curves for aSMR
```{r SMR curves}
species <- species <- c("Pl","Fd", "Lw")
minNumPlots <- 10 ##remove bins where there are few plots in total
brk <- seq(0,8,length.out = 17)
matHistAll <- hist(SMRdat$aSMR, breaks = brk,plot = T) ##create histogram of all plots for specified variable
histAll <- matHistAll$counts

out <- foreach(sppCode = species,.combine = c) %do% {
    spp <- sppLookup$Code[sppLookup$TreeCode == sppCode]
    
    brk <- seq(0,8,length.out = 17)
    veg <- vegAll[Species == spp,.(PlotNumber,Species,Cover)]
    veg <- SMRdat[veg, on = "PlotNumber",nomatch = 0]
    veg <- veg[complete.cases(veg),]

    vegHist <- wtd.hist(veg$aSMR, plot = F,weight = veg$Cover, breaks = brk)
    
    brk <- brk[histAll > minNumPlots]
    h <- vegHist$counts[histAll > minNumPlots]/histAll[histAll > minNumPlots] ##ratio of weighted veg hist to total num plots in each bin
    if(length(brk) > length(h)){brk <- brk[-1]} ##depending on the variable sometimes breaks don't line up
    
    dat <- data.frame(x = brk, r = h) ##create data for nls
    muStart <- brk[h == max(h) ] ###starting values for optimisation
    sdStart <- muStart/4
    kStart <- muStart/2
    aStart <- 10
    
    fit <- nlsLM(r ~ k * dsn(x,xi = mu,omega = sigma, alpha = a), start=c(mu=muStart,sigma=sdStart,k=kStart,a = aStart) , # a=0
                 data = dat)
    v <- summary(fit)$parameters[,"Estimate"] ###v contains the 4 parameters for the best fit curve
    mX <- optimize(plotNrm, interval = c(min(dat$x-10),max(dat$x + 10)), maximum = T) ##find maximum
    probMx <- psn(mX$maximum,xi = v[1],omega = v[2],alpha = v[4]) ##find area below maximum
    plotNrm <- function(x) {v[3] * dsn(x, v[1],v[2],v[4])}
    
    quants <- qsn(c(probMx/10,probMx/2,probMx+(1-probMx)*0.5,probMx+(1-probMx)*0.9),xi = v[1],omega = v[2],alpha = v[4])
    quants <- c(min(dat$x-10),quants,max(dat$x + 10))
    if(quants[1] > quants[2]){quants[1] <- quants[2]-10}
    if(quants[6] < quants[5]){quants[6] <- quants[5]+10}
    lims <- qsn(c(0.01,0.99),xi = v[1],omega = v[2],alpha = v[4])
    
    p1 <- ggplot(dat)+
      geom_point(aes(x = x, y = r),color = "black")+
      #stat_function(fun = plotNrm, colour = "black")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[3],quants[4],0.1)),x = seq(quants[3],quants[4],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "green")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[2],quants[3],0.1)),x = seq(quants[2],quants[3],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[4],quants[5],0.1)),x = seq(quants[4],quants[5],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[1],quants[2],0.1)),x = seq(quants[1],quants[2],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
      geom_ribbon(data = data.frame(y = plotNrm(seq(quants[5],quants[6],0.1)),x = seq(quants[5],quants[6],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
      xlim(lims)+
      ylim(c(0,NA))+
      labs(y = "Standardised Frequency",x = "aSMR", title = paste(spp, "aSMR"))+
      theme_few()
    
    list(p1)
}
grid.arrange(grobs = out, ncol = 2) ##plot

```

### SNR

```{r snr curve}
species <- species <- c("Pl","Fd","Sx","Py")
SMRdat <- SMRdat[NutrientRegime != "F",]
SMRdat$NutrientRegime <- as.factor(SMRdat$NutrientRegime)
matHistAll <- barplot(table(SMRdat$NutrientRegime)) ##create histogram of all plots for specified variable
histAll <- table(SMRdat$NutrientRegime)

par(mfrow = c(2,2))

foreach(sppCode = species,.combine = c) %do% {
    spp <- sppLookup$Code[sppLookup$TreeCode == sppCode]
    
    veg <- vegAll[Species == spp,.(PlotNumber,Species,Cover)]
    veg <- SMRdat[veg, on = "PlotNumber",nomatch = 0]
    veg <- veg[complete.cases(veg),]

    vegHist <- veg[,.(CovSum = sum(Cover)), by = NutrientRegime]
    setorder(vegHist,NutrientRegime)
    h <- vegHist$CovSum/histAll
    
    barplot(h,xlab = "SNR",ylab = "Standardised Cover", main = spp)
    NULL
}
```





###Old Code -- to do each one individually###

```{r species by variable}
## lower limit of these variables: DD5_sm, 

var = "Tmax_sm"
brk <- seq(min(vegAll[[var]]),max(vegAll[[var]]),length.out = 40)
matHistAll <- hist(vegAll[[var]], breaks = brk) ##create histogram of all plots for specified variable
histAll <- matHistAll$counts

###now for specified species
spp = "PINUCON"
sppCode = "Pl"
veg <- vegAll %>% filter(Species == spp) %>% droplevels()# & PlotNumber %in% vegAll$PlotNumber,]
#veg <- veg[Tmax_sm > -10,]
#veg <- veg[!duplicated(veg, by = "PlotNumber"),]
#veg <- veg[,c(1:13,19,14:18),with = F]
#veg <- removeOutlier2(dat = veg, alpha = 0.01, numIDvars = 7) ###also remove outliers once it's just plots containing said species
dat <- veg
numIDvars = 7
alpha = .01
md <- mahalanobis(dat[,-c(1:numIDvars)],
                       center = colMeans(dat[,-c(1:numIDvars)]), 
                       cov = cov(dat[,-c(1:numIDvars)]))

ctf <- qchisq(1-alpha, df = ncol(dat)-1)
outl <- which(md > ctf)
dat <- dat[-outl,]
veg <- dat

matHistspp <- hist(veg[[var]], breaks = brk) ##create histogram of all plots for specified variable
```

```{r distribution of species across variables}
vegHist <- wtd.hist(veg[[var]], plot = T,weight = veg$Cover, breaks = brk)
minNumPlots <- 10 ##remove bins where there are few plots in total
brk <- brk[histAll > minNumPlots]
h <- vegHist$counts[histAll > minNumPlots]/histAll[histAll > minNumPlots] ##ratio of weighted veg hist to total num plots in each bin
if(length(brk) > length(h)){brk <- brk[-1]} ##depending on the variable sometimes breaks don't line up

plot(h ~ brk)
dat <- data.frame(x = brk, r = h) ##create data for nls
muStart <- brk[h == max(h) ] ###starting values for optimisation
sdStart <- muStart/4

#nrm <- formula(r ~ k*exp(-1/2*(x-mu)^2/sigma^2))

###non-linear least squares fit for optimal parameters
###note that we have to multiply the dsn function by a constant, otherwise integrates to 1
###Occasionally the nls algorithm gets stuck if the starting values aren't close enough - if this happens, try and make the initial values better
fit <- nlsLM(r ~ k * dsn(x,xi = mu,omega = sigma, alpha = a), start=c(mu=muStart,sigma=sdStart,k=muStart,a = 1) , # a=0
             data = dat)
v <- summary(fit)$parameters[,"Estimate"] ###v contains the 4 parameters for the best fit curve
```

##set up BGC subzone data
note that you can adjust the neutral parameters in the aspectRation function
green = 1, yellow = 2, red = 3, brown = 4,5 or NA
```{r Environmental space of BGCs aspect adjusted}
bgcDat <- fread("WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv")
var <- "Tmax_sm"
bgDat <- bgcDat[,c("BGC","Latitude",var), with = F]
colnames(bgDat)[3] <- "Var"
##remove outliers
bgDat <- bgDat[, 
    .SD[(Var < quantile(Var, probs = 0.90)) & ((Var > quantile(Var, probs = 0.10)))
    ], by = BGC
]


t1 <- aspectRatio(lat = bgDat$Latitude, slope = 30, aspect = 135)
bgDat$Neutral <- bgDat$Var*t1 ###"neutral" aspect
t1 <- aspectRatio(lat = bgDat$Latitude, slope = 30, aspect = 225)
bgDat$Warm <- bgDat$Var*t1 ###"warm" aspect

bgAvg <- bgDat[,.(MeanCld = mean(Var),MeanWrm = mean(Warm)), by = "BGC"]

suit <- fread("Feasibility_v11_21.csv")
suit <- suit[Spp == sppCode,.(BGC,SS_NoSpace,Spp,Feasible)]
suit <- suit[grep(".*01|.*101",SS_NoSpace),.(BGC,Feasible)]
cols <- data.table(Feasible = c(1,2,3,4,5),col = c("green","yellow","red","brown","brown"))
suit2 <- suit[cols, on = "Feasible", nomatch = 0]
###select units to display
bgDat <- bgDat[BGC %in% c("BAFAun", "BWBSdk", "ESSFmc", "SBSdk", "SBSmc2", "ICHmc2","ICHmc1", "SBSdw3", "IDFdk3", "PPxh1"),]
bgDat <- bgDat[order(BGC),]

cols <- data.table(BGC = unique(bgDat$BGC))
cols <- suit2[cols, on = "BGC"]
cols$col[is.na(cols$col)] <- "brown"

library(ggthemes)

###horizonal boxplot
clim <- ggplot(bgDat)+
  geom_boxploth(aes(x = Neutral, y = BGC, group = BGC),colour = cols$col)+
  geom_boxploth(aes(x = Warm, y = BGC, group = BGC),colour = cols$col)+
  geom_boxploth(aes(x = Var, y = BGC, group = BGC),colour = cols$col)+
  #xlim(c(min(dat$x-10),max(dat$x + 10)))+
  labs(y = "BGC", x = var)+
  theme_few()

plot(clim)
```


##function to plot best fit skewed normal
```{r build species curves}
plotNrm <- function(x) {v[3] * dsn(x, v[1],v[2],v[4])}
mX <- optimize(plotNrm, interval = c(min(dat$x-10),max(dat$x + 10)), maximum = T) ##find maximum
probMx <- psn(mX$maximum,xi = v[1],omega = v[2],alpha = v[4]) ##find area below maximum
##set up quantiles for colouring
quants <- qsn(c(probMx/10,probMx/2,probMx+(1-probMx)*0.5,probMx+(1-probMx)*0.9),xi = v[1],omega = v[2],alpha = v[4])
quants <- c(min(dat$x-10),quants,max(dat$x + 10))
if(quants[1] > quants[2]){quants[1] <- quants[2]-10}
if(quants[6] < quants[5]){quants[6] <- quants[5]+10}
lims <- qsn(c(0.001,0.999),xi = v[1],omega = v[2],alpha = v[4])

bgAvg <- bgAvg[suit, on = "BGC"]
bgAvg <- bgAvg[!is.na(MeanCld),]
ctfLow <- min(bgAvg$MeanCld[bgAvg$Feasible == 1])
horizLow <- plotNrm(ctfLow)
ctfHigh <- max(bgAvg$MeanWrm[bgAvg$Feasible == 1])

##plot response curve
p1 <- ggplot(dat)+
  geom_point(aes(x = x, y = r),color = "black")+
  stat_function(fun = plotNrm, colour = "black")+
  geom_ribbon(data = data.frame(y = plotNrm(seq(quants[3],quants[4],0.1)),x = seq(quants[3],quants[4],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "green")+
  geom_ribbon(data = data.frame(y = plotNrm(seq(quants[2],quants[3],0.1)),x = seq(quants[2],quants[3],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
  geom_ribbon(data = data.frame(y = plotNrm(seq(quants[4],quants[5],0.1)),x = seq(quants[4],quants[5],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "yellow")+
  geom_ribbon(data = data.frame(y = plotNrm(seq(quants[1],quants[2],0.1)),x = seq(quants[1],quants[2],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
  geom_ribbon(data = data.frame(y = plotNrm(seq(quants[5],quants[6],0.1)),x = seq(quants[5],quants[6],0.1)), aes(ymin = 0,ymax = y,x =x), alpha = 0.5, fill = "red")+
  geom_vline(xintercept = ctfLow)+
  geom_vline(xintercept = ctfHigh)+
  geom_hline(yintercept = horizLow)+
  xlim(lims)+
  ylim(c(0,NA))+
  labs(y = "Standardised Frequency", title = paste(spp, var))+
  theme_few()+
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())

p2 <- ggplot(bgDat)+
  geom_boxploth(aes(x = Neutral, y = BGC, group = BGC),colour = cols$col)+
  geom_boxploth(aes(x = Warm, y = BGC, group = BGC),colour = cols$col)+
  geom_boxploth(aes(x = Var, y = BGC, group = BGC),colour = cols$col)+
  xlim(lims)+
  geom_vline(xintercept = ctfLow)+
  geom_vline(xintercept = ctfHigh)+
  labs(y = "BGC", x = var)+
  theme_few()
ggplot_build(p2)$data[[1]]
###stack vertically using cowplot library
cowplot::plot_grid(p1, p2, align = "v", ncol = 1, rel_heights = c(0.66, 0.34))
```










