---
title: "TreeSpeciesRanking"
author: "William H MacKenzie"
date: "02/10/2019"
output: html_document
---

# Tree Species Environmental Suitability  - March 16, 2019

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require (RGtk2)
require(plyr)
require (rChoiceDialogs)
require (data.table)
require(doBy)
require (utils)
require(labdsv)
require(tools )
require(svDialogs)
require(tcltk)
require(randomForest)
require(foreach)
require(dplyr)
require(reshape2)
require(reshape)
require(doParallel)
require(caret)
require(C50)
require (stringr)
require(UBL)
require(dostats)
require(ordinalForest)
require(tidyverse)
require(ggplot2)
require (RGtk2)

require (rgdal)
require(mapview)
require(sf)
require(tmap)
require(tidyverse)
require(rmapshaper)
require(rgeos)
require(raster)
require(devtools)
#require(cleangeo)

options(stringsAsFactors = FALSE)
## set up some folder location variables
outputs <- ("./outputs/") # location of model outputs 
inputs <- ("./inputs/") 
DB_share <- ("C:/Users/whmacken/Dropbox (WorkingFiles_Telus)/Suitability Review/")
common <- ("D:/CommonTables/TreeFeasibility/")
```

## Import working Esuitability ratings table

Table contains all site units for western north america.
```{r import working Esuitability, include=FALSE}

ESuit <- fread(paste0(common, "./Feasibility_v11_22.csv"), data.table = FALSE)
WNA_BGC <- fread ("D:/CommonTables/BECdb/All_BGCs_v11_20.csv", data.table = FALSE)
BC_BGC <- WNA_BGC %>% filter(DataSet == "BC") %>% dplyr::select(Map_Label) %>% dplyr::rename("BGC" = Map_Label)
ESuit <- left_join(BC_BGC, ESuit)
# #ESuit$ESuit <- paste ("E", ESuit$ESuit, sep = "")
# #ESuit <- ESuit[!(ESuit$ESuit == "E5"),]
 ESuit <- ESuit %>% dplyr::select(BGC, SS_NoSpace, Spp, SppVar, Feasible) %>% distinct()
 
 BECv12 <- fread(paste0(inputs, "./BECv12_newunits.csv"), data.table = FALSE)
 
 BECv12 <- left_join(BECv12, ESuit)
 write.csv (BECv12 , paste0 (outputs,"BECv12_newunitFeasibility.csv"), row.names = FALSE )
```


## Merge in Reference Guide ratings and footnootes for comparison

```{r import reference guide}
RefGuide <- fread ("D:/CommonTables/ReferenceGuide/ReferenceGuide2019Complete_update2.csv",stringsAsFactors=FALSE)
RefGuide <- RefGuide %>% dplyr::select(Region,ZoneSubzone,SS_NoSpace, Species, Suitability, Standard, FN1, FN2, FN3, FN4, FN5, FN6) %>% dplyr::rename(BGC = ZoneSubzone, Spp = Species)
   #RefGuide <- drop_na(RefGuide)
### limit refguide to only those units listed in the BECdb
    BECdb <- fread ("D:/CommonTables/BECdb/WNA_SSeries_v11_20.csv", stringsAsFactors=FALSE)
    BECdb <- drop_na(BECdb)
###read in accepted units BECv11
RefGuide <- RefGuide[RefGuide$SS_NoSpace %in% BECdb$SS_NoSpace,]
### remove the climate change Standards entries
RefGuide <- RefGuide %>% dplyr::filter(!grepl('CC', Standard))
##update species codes in Ref guide
RefGuide$SppVar <- RefGuide$Spp 
RefGuide$Spp <- RefGuide$Spp %>% dplyr::recode("Se" = "Sx", "Sw" = "Sx", "Sxw" = "Sx", "Pli" = "Pl", "Plc" = "Pl", "Fdc" = "Fd", "Fdi" = "Fd", "Acb" = "Ac", "Act" = "Ac", "Pyc" = "Py", "Pyi" = "Py")
#RefGuide <- RefGuide[,c(2:4,9:15)]
#RefCombine <- RefGuide[,c(1:3)]
FullSuitCompare <- left_join(ESuit, RefGuide, by.x= c("BGC","SS_NoSpace", "Spp"), by.y = c("BGC","SS_NoSpace", "Spp"), all = TRUE) ##usually set to TRUE
#FullSuitCompare <- FullSuitCompare[(FullSuitCompare$Region == "Nelson") | (FullSuitCompare$Region == "LMH71") | (FullSuitCompare$Region == "LMH702016"), ]
FullSuitCompare <-  FullSuitCompare  %>% distinct()

###This section simply write a comparison between the reference guide and a table of new ESUITs for review
FullSuitCompare2 <- FullSuitCompare
FullSuitCompare2$Feasible_Ref_same <- FullSuitCompare2$Feasible == FullSuitCompare2$Suitability

colnames(FullSuitCompare2)
data = FullSuitCompare2 %>% dplyr::select(Region, BGC, SS_NoSpace, Standard, Spp, SppVar, Suitability, Feasible, Feasible_Ref_same, FN1, FN2, FN3, FN4, FN5, FN6, everything())
#data <- data[!(data$Region == "NA"),]
write.csv (data, paste0 (outputs,"ReferenceGuide&ESuit2.csv"), row.names = FALSE )
```
########Bring in Footnote Lookup table
add restriction type variables
```{r footnote type}
footnotes <- fread ("./inputs/FootnoteType.csv")
refguide_footnotes <- data %>% dplyr::select (FN1, FN2, FN3, FN4, FN5, FN6) #as.data.frame (FullSuitCompare[, 19:23])
### converts footnote numbers into a series of footnote types
for ( j in colnames(refguide_footnotes)) { # need to check if these columns align to Footnote columns
for(i in 1: nrow(footnotes)){
  c <- as.integer(footnotes[i,1])
  d <- as.character (footnotes[i,2])
  data [[j]] [data [[j]] == c] <- d
  }
}
data$cold_limit <- apply(data == "cold", 1, any)
data$heat_limit <- apply(data == "heat", 1, any)
data$drought_limit <- apply(data == "drought", 1, any)
data$wet_limit <- apply(data == "wet", 1, any)
data$geographic_limit <- apply(data == "geographic", 1, any)
data$trial_spp <- apply(data == "trial", 1, any)
data <- data %>% dplyr::select(-FN1, -FN2, -FN3, -FN4, -FN5, -FN6)

FullSuitCompare <- merge (data, refguide_footnotes, by = 0) # add back in the original FN numbers
#ESuit <- rbind (ESuit, ESuit4) ### use where combining multiple suitability sheets
FullSuit.list <- unique(FullSuitCompare$Unit)

write.csv (FullSuitCompare, paste0 (outputs,"CFRG_Feasibility_w_Footnotes.csv"), row.names = FALSE )
```


## Generate site level CMD from climate surface derived data
LHC_training set is generated from ##### script
```{r import climate}
X1 <- fread("./InputData/WNA_4k_HexPts_BGC_Normal_1961_1990MSY.csv", data.table = FALSE, stringsAsFactors=FALSE)
colnames (X1)[2] <- "BGC"
X1 <- X1[-1]
# ####Prepare additional variables
X1$PPT_MJ <- X1$PPT05 + X1$PPT06 # MaY/June precip
X1$PPT_JAS <- X1$PPT07 + X1$PPT08 + X1$PPT09 # July/Aug/Sept precip
X1$PPT.dormant <- X1$PPT_at + X1$PPT_wt # for calculating spring deficit
X1$CMD.def <- 500 - (X1$PPT.dormant)# start of growing season deficit original value was 400 but 500 seems better
X1$CMD.def [X1$CMD.def < 0] <- 0 #negative values set to zero = no deficit
X1$CMD.grow <- X1$CMD05 + X1$CMD06 +X1$CMD07 +X1$CMD08 +X1$CMD09
X1$DD5.grow <- X1$DD5_05 + X1$DD5_06 + X1$DD5_07 + X1$DD5_08 + X1$DD5_09
X1$CMD.total <- X1$CMD.def + X1$CMD
X1$CMDMax <- X1$CMD07 # add in so not removed below
X1$DDgood <- X1$DD5 - X1$DD18
X1$DDnew <- (X1$DD5_05 + X1$DD5_06 +X1$DD5_07  + X1$DD5_08)  - (X1$DD18_05 + X1$DD18_06 +X1$DD18_07 +X1$DD18_08)
X1$TmaxJuly <- X1$Tmax07
#

VarList = c("bFFP","CMD.total","DD5","EMT", "EXT","FFP","MSP","Eref","Tave07","PAS","Tmin_wt","CMDMax")

X1 <- X1 %>% dplyr::select(BGC, VarList)
# modelvars <- read.csv (as.character("./outputs/Final23Var_WNABGCv11.csv"))
# modelvars <- as.character(modelvars$x)


CMD <- aggregate( CMD.total ~ BGC, X1, mean) ##
meanVar <-aggregate( . ~ BGC, X1, mean)
SS_Var <- merge(ESuit, meanVar, by = "BGC")
SS_Var$Spp [is.na(SS_Var$Spp)] <- "X" ### where no treespecies suitable create a no-species code 'X'

###_____________________________________________####

###for each wetter rSMR, previous CMD is divided by 2
# for (i in 1:3){
#   CMD[,2+i] <- CMD[,1+i]/2
# }
# colnames(CMD) <- c("BGC","4","5","6","7")
# CMD <- CMD[,c(1,3:5,2)]
#
# ###for each drier rSMR, previous CMD + 100
# for (i in 1:4){
#   CMD[,length(CMD)+1] <- CMD[,length(CMD)] + 100
# }
# colnames(CMD)[6:9] <- c("3","2","1","0")
#
# CMD <- CMD[,order(colnames(CMD))]## creates full grid of CMD values by BGC by rSMR class
#
# CMD.list <- melt(CMD)
#  #######needs to get rid of blank BGC
# CMD.list$EDA <- paste (CMD.list$BGC, "_", CMD.list$variable)
# CMD.list <- CMD.list[,-c(1:2)]
```


## Import edatopic and aSMR tables

Merge all climate and edatopic variables with suitability ratings

```{r import edaphic}

E1 <- fread (paste0("./inputs/Edatopic_v11_22.csv"),stringsAsFactors=FALSE , na.strings= c("", "NA"))
# 
# #E2 <- E1 %>% distinct()
# #write.csv (E2, "Edatopic_v11.2.csv")
# #E1 <- E1[,-c(5)]
# #E1 <- E1 [is.na (E1$Codes),]### removes site series flagged with special condition
# E1 <- unique(E1)
# Codes <- unique (E1[,c(3,6)]) ## identify special ecosystems
# colnames (Codes) [1] <- "Unit"
# 
# E1$SNR <-str_sub(E1$Edatopic, 1,1)
# E1$rSMR <-str_sub(E1$Edatopic, -1,-1)
# E1$EDA <- paste (E1$MergedBGC, "_", E1$rSMR)
# E1_sub <- E1 [E1$EDA %in% CMD.list$EDA,]
# E1_sub <- merge (E1_sub, CMD.list, by = "EDA")
# names(E1_sub) [10] <- "EdaCMD"
# E1_sub$EdaCMD <- as.numeric(E1_sub$EdaCMD)
# E2 <- E1_sub
# #E1_sub$SNR <- as.factor(E1_sub$SNR)
# E1_sub$SNR_num <- E1_sub$SNR%>% str_replace_all(c("A" = "1", "B" = "2", "C" = "3", "D" = "4" ,"E" = "5" ))
# E1_sub$SNR_num <- as.numeric(E1_sub$SNR_num)
# 
#  
# aSMRrSMR = "./inputs/modelled_ALLv11_rSMR_aSMR_grid_HalfStep.csv"
# aSMR <- fread(aSMRrSMR,stringsAsFactors=FALSE,na.strings=".")
# aSMR <- aSMR[,-1]
# colnames(aSMR) <- c("BGC","0","1","2","3","4","5","6","7")
# aSMR.list <- melt(aSMR)
# aSMR.list$EDA <- paste (aSMR.list$BGC, "_", aSMR.list$variable)
# aSMR.list <- aSMR.list [,-c(1:2)]
# E1_sub <- merge (E1_sub, aSMR.list, by = "EDA")
# colnames (E1_sub)[12] <- "aSMR"
# E1_sub <- E1_sub [, c("SS_NoSpace", "EdaCMD", "SNR_num", "aSMR")]#
# E1_sub <- E1_sub %>% distinct()
# E1_sub$SS_NoSpace <- as.character(E1_sub$SS_NoSpace)
# SS_data <- E1_sub[,-1] %>% group_by(E1_sub$SS_NoSpace) %>% summarise_all(list(~min(.),~mean(.),~max(.), ~sd(.)))###ignore warning
# #SS_data <- SS_data [-2]
# colnames(SS_data)[1] <- "SS_NoSpace"
# SS_test <- merge (SS_Var, SS_data, by = "SS_NoSpace")
# difs <- setdiff(SS_Var$SS_NoSpace,SS_data$SS_NoSpace) ### look for units no matching between 2 tables
# difs
# #difs2 <- setdiff(SS_data$Unit,SS_Var$Unit)
# #difs2
# SS_test <- SS_test[!is.na(SS_test$Spp),]
# SS_test$ES_RG_same <- SS_test$ESuit == SS_test$RefSuit
# data = SS_test %>% select(Region, BGC, Unit, Spp, ESuit, RefSuit, ES_RG_same,
#                           cold_limit, heat_limit,drought_limit,wet_limit, geographic_limit, 
#                           FN1, FN2, FN3, FN4, FN5,
#                          EdaCMD_max, aSMR_min, aSMR_max, Tmin_sp,  bFFP, PAS)
# data <- data %>% distinct()
# write.csv (data, "./outputs/SS_Suit_for_Review.csv")
```

### Compare to  A Banners original ratings
Limit to Esuit rating he provided.
Add in flag variable to show where differs from current ratings

``` {r merge with draft suitability ratings - ABanner}
# 
# AB_Suit <- fread("./inputs/TreeSppSuit_v10.10_AB.csv")
# AB_Suit.list <- melt(AB_Suit)
# colnames (AB_Suit.list) [2:3] <- c("Spp", "AB_suit")
# AB_Suit.list <- AB_Suit.list %>% drop_na()
# SS_test2 <- merge (SS_test, AB_Suit.list, by = c("Unit", "Spp"))
# SS_test2$ES_AB_same <- SS_test2$ESuit == SS_test2$AB_suit
# SS_test2$ES_RG_same <- SS_test2$ESuit == SS_test2$RefSuit
# colnames(SS_test2)
# data = SS_test2 %>% select(BGC, Unit, Spp, ESuit, AB_suit, ES_AB_same, RefSuit, ES_RG_same, 
#                           cold_limit, heat_limit,drought_limit,wet_limit, geographic_limit,
#                           FN1, FN2, FN3, FN4, FN5,
#                          EdaCMD_max, aSMR_min, aSMR_max, Tmin_sp,  bFFP, PAS)
# data <- data %>% distinct()
# 
# write.csv (data, "./outputs/ESuit_review_AB.csv")
```




## Estimated relative site index (by site condition)

Need input table of relative site index by aSMR x SNR
Add the SI % value to each edatopic position in E1 for each species
Turn into actual Site Index Values by multiplying by GDD based factor
Summarize by site series (mean plus SD)


``` {r estimated site index}
# rSI <- fread ("./inputs/rSI_by_Edatope.csv") # this is a heuristic approximation of relative site index on a absolute grid
# <<<<<<< HEAD
# rSI$aEdatopic <- paste0(rSI$SNR, rSI$aSMR)
# rSI <- as.data.frame (rSI)
# DD5 <- fread ("./inputs/DD5_BGC.csv") # growing degree days by BGC
# E2_sub <- merge (E2, aSMR.list, by = "EDA")
# colnames (E2_sub)[11] <- "aSMR"
# E2_sub$aEdatopic  <- paste0(E2_sub$SNR, E2_sub$aSMR)
# setnames(E2_sub, "MergedBGC", "BGC")
# # add in DD5 values by BGC
# E2_sub <- left_join(E2_sub, DD5, by = "BGC")
# 
# spps <- unique(rSI$Spp)
# BGCs <- unique (E2_sub$MergedBGC)
# #spp = "Fd"
# ####need to change into a foreach and the rbind to get final table
# for (spp in spps){
#   SS.temp <- ESuit$Unit[ESuit$Spp == spp]
#   Suit.temp <- E2_sub [E2_sub$SS_NoSpace %in% SS.temp,]
#   rSI.temp <- rSI [,c(4:5)] [rSI$Spp %in% spp,]
#   Suit.temp <- left_join(Suit.temp, rSI.temp, by = "aEdatopic")#  ### add in rSI values to each line
#   Suit.temp$SI <- Suit.temp$rSI *(Suit.temp$DD5 * 0.022)  ### multiply rSI * formula to new variable to get SI
#   ### Need to adjust for excessive heat limitations to growth
#   Suit.temp <- Suit.temp %>% 
#   select(BGC, SS_NoSpace, SI)
#   SI.temp <- Suit.temp [-2] %>% group_by(Suit.temp$SS_NoSpace) %>% summarise ( SI_mean = mean(SI), SI_sd = sd(SI)) 
#   SI.temp$Spp <- spp
# 
# }
# 
# 
# # formula for SI = rSI * (DD5 *.022)relative SI into a SI50 value for Fd
# 
# DD5 <- fread ("./inputs/DD5_BGC.csv") # growing degree days by BGC
# E2_sub <- merge (E2, aSMR.list, by = "EDA")
# colnames (E2_sub)[11] <- "aSMR"
# 
# spps <- unique(rSI$Spp)
# BGCs <- unique (E2_sub$MergedBGC)
# spp = "Fd"
# for (spp in spps){
#   SS.temp <- ESuit$Unit[ESuit$Spp == spp]
#   Suit.temp <- E2_sub [E2_sub$SS_NoSpace %in% SS.temp,]
#   ### add in RSI values to each line
#   ### multiply RSI * formula to new variable to get SI
#   ###summarize SI by site series mean and sd
#   
#   
#   
#   for(edatope in edatopes){
#     comm.ref <- get(paste("comm.ref", edatope, sep=""))
#     comm.ref.spp <- comm.ref>0
#     
#     for(rcp in rcps){
#       for(proj.year in proj.years){
# 
#         comm.proj <- as.data.frame(matrix(rep(NA, dim(points)[1]*length(spps)), dim(points)[1], length(spps)))
#         for(spp in spps){
#           Suit <- read.csv(paste("outputs/Suit", grid, GCM, rcp, proj.year, spp, edatope, "csv", sep="."))[,1]
#           Suit[Suit==4] <- 5
#           Suit <- 1-(Suit-1)/4
#           comm.proj[,which(spps==spp)] <- Suit
#         }    
#     
#     
# 
# 
# E2_sub2 <- E2_sub2[E2_sub$MergedBGC %in% ESuit$Unit[ESuit$Spp == "Fd"]] <- rSI$rSI
# E1_sub <- E1_sub [, c("SS_NoSpace", "EdaCMD", "SNR_num", "aSMR")]#
# E1_sub <- E1_sub %>% distinct()
# E1_sub$SS_NoSpace <- as.character(E1_sub$SS_NoSpace)
# E2 <- merge(E1, )
# SS_edatope <- 
#Add the equivalent aSMR to rSI
# formula for SI = rSI * (DD5 *.022)relative SI into a SI50 value

```

## Create edatopic grid review materials 

On edatopic grid show species suitable by edatopic position
Suitability rating
Site Index
aSMR

```{r Edatopic Review}
# SIdat <- fread("./inputs/BartPredSI.csv", data.table = F)
# edaDat <- fread("./inputs/Edatopic_v11_7.csv", data.table = F)
# edaDat <- edaDat[edaDat$Source %in% c("BECv10","BECv11"),c("MergedBGC", "SS_NoSpace","Edatopic")]
# suitDat <- fread("./inputs/TreeSpp_ESuit_v11_18.csv", data.table = F)
# suitDat <- suitDat[suitDat$Unit %in% unique(edaDat$SS_NoSpace),c("Unit","Spp","ESuit")]
# SIdat <- SIdat[,-4]
# 
# dat <- merge(SIdat, suitDat, by = c("Unit","Spp"), all = T)
# dat <- dat[!is.na(dat$SIPred),]
# dat <- dat[!is.na(dat$ESuit) | dat$SIPred >= 20,]
# dat$ESuit[is.na(dat$ESuit)] <- 5
# colnames(edaDat) <- c("Subzone","Unit","Edatopic")
# edaDat <- unique(edaDat)
# dat <- merge(dat, edaDat, by = "Unit", all.x = T)
# dat$SIPred <- round(dat$SIPred,1)
# dat <- unique(dat)
# dat <- dat[!is.na(dat$Edatopic),]
# 
# 
# out <- foreach(BGC = unique(dat$Subzone), .combine = rbind) %do% {
#   sub <- dat[dat$Subzone == BGC,]
#   gridDat <- foreach(eda = unique(sub$Edatopic), .combine = rbind) %do% {
#     sub2 <- sub[sub$Edatopic == eda,]
#     temp <- aggregate(cbind(SIPred, ESuit) ~ Spp + Edatopic, sub2, FUN = mean) %>%
#       mutate(SIPred = round(SIPred,1), ESuit = round(ESuit, 0))
#     temp <- temp[order(-temp$SIPred),]
#     temp$Spp <- paste(temp$Spp,temp$SIPred, sep = ":")
#     if(any(temp$ESuit == 1)){
#       dom <- paste(temp$Spp[temp$ESuit == 1], collapse = ",")
#       dom <- paste("*",dom,"*\n", sep = "")
#     }else{
#       dom <- NULL
#     }
#     if(any(temp$ESuit == 2)){
#       sec <- temp$Spp[temp$ESuit == 2]
#       sec <- paste(sec, collapse = ",")
#       sec <- paste(sec,"\n")
#     }else{
#       sec <- NULL
#     }
#     if(any(temp$ESuit == 3)){
#       un <- temp$Spp[temp$ESuit == 3]
#       un <- paste(un, collapse = ",")
#       un <- paste("(",un,")\n", sep = "")
#     }else{
#       un <- NULL
#     }
#     if(any(temp$ESuit %in% c(4,5))){
#       x <- temp$Spp[temp$ESuit %in% c(4,5)]
#       x <- paste(x,",",sep = "")
#       if(length(x) >= 2){
#         j <- 0
#         for(i in seq(2,length(x), by = 2)){x <- append(x,"\n", after = i+j);j <- j+1}
#       }
#       if(x[length(x)] == "\n"){x <- x[-length(x)]}
#       x <- paste(x, collapse = "")
#       x <- paste("[",x,"]", sep = "")
#     }else{
#       x <- NULL
#     }
#     lab <- paste(dom, sec,  un,x, sep = "")
#     
#     data.frame(Edatopic = eda, Label = lab)
#   }
#   gridDat$Alpha <- gsub("[[:digit:]]","",gridDat$Edatopic)
#   gridDat$Numeric <- gsub("[[:upper:]]","",gridDat$Edatopic) %>% as.numeric()
#   ##plot
#   pdf(file = paste("./outputs/SIGrid_",BGC,".pdf",sep = ""), height = 10.5, paper = "letter")
#   print(ggplot(data = gridDat)+
#           geom_tile(aes(x= Alpha, y = Numeric), color = "black", fill = "white")+
#           geom_text(aes(x = Alpha, y = Numeric, label = Label), size = 2.4)+
#           scale_y_discrete(limits = c("8","7","6","5","4","3","2","1","0"))+
#           scale_x_discrete(limits = c("A","B","C","D","E"))+
#           labs(x = "Relative Soil Nutrient Regime", y = "Relative Soil Moisture Regime", cex = 1.5, title = BGC)+
#           theme_bw(base_size = 10)+
#           theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
#           coord_fixed())
#   dev.off()
#   gridDat
# }


## export spatial file suitability rating for review of CCISS paper 
```

```{r review maps}
# SS_Use <- fread("D:/CommonTables/BECdb/SiteSeries_Use_CCISSpaper_24Mar2020.csv", data.table = FALSE)
# SS_D6 <-SS_Use %>% filter(Use == "D6")
# ###Compare to list of BGCs modelled
# BGC_Use <- fread("D:/CommonTables/BECdb/All_BGCs_v11.csv")
# compare <- anti_join(BGC_Use, SS_Use, by = c("Map_Label" = "BGC"))
# compare2 <- anti_join(SS_Use, BGC_Use,  by = c("BGC" = "Map_Label" ))
# # Edatopic <- fread("D:/CommonTables/BECdb/Edatopic_v11_20.csv")
# # compare3 <- anti_join(BGC_Use, Edatopic, by = c("Map_Label" = "BGC"))
# # Edatopic$num <- "1"
# # Edawet <- Edatopic %>% filter(Edatopic %in% c("D6","D5","D7")) %>%
# #     dplyr::select(SS_NoSpace,Edatopic, num) %>%
# #     pivot_wider(names_from = Edatopic, values_from = num)
# # Edawet1 <- Edawet[!(is.na(Edawet$D6)),]
# # fwrite(Edawet1, "./outputs/wetsiteseries.csv")
# 
# SS.list <- as.list(SS_Use$SS_NoSpace)
# #SS_C4 <- SS_Use[SS_Use$Use == "C4",]
# #SS_Use$SS_NoSpace <-  as.character(SS_Use$SS_NoSpace)
# CCISS_ESuit <- ESuit [ESuit$SS_NoSpace %in% SS.list,]
# CCISS_ESuit <- CCISS_ESuit %>% dplyr::select(SS_NoSpace, Spp, ESuit) %>%
#     full_join(.,SS_Use)%>%
#     dplyr::select(-Source, -Edatopic) %>% dplyr::select(BGC, everything()) %>% 
#     distinct()
# fwrite(CCISS_ESuit, "./outputs/ESuit_CCISSPaper_full.csv")

```